About the Beamer class in presentation making

### 2020-06-27 latex/slides/slides.tex
Update slides

%---------------------------------------------------------
\section{BERT}

@@

  \begin{itemize}
    \item BERT base was used;
          \begin{itemize}
            \item 12 layers;
          \end{itemize}
    \item Hugging Face and PyTorch was used;
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Adam;
          \begin{itemize}
            \item Adam epsilon: \num{1e-4};
          \end{itemize}
    \item Batch size: \num{10};
    \item Training epochs: \num{10.5};
    \item Beam search hypothesis: \num{3};
  \end{itemize}
\end{frame}

@@

  \begin{table}
    \scriptsize
    \begin{tabularx}{\textwidth}{|X|X|c|c|}
      \hline
      \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?} & \textbf{Correct?} \\
      \hline
      Let me know if this works.                                                                                                                                                                            & This works great. Will let you know. as soon as I get a chance, let me know                                                                                                                                                        & \num{0}{\%}  & yes               \\
      \hline
      Following are the terms under which I ran the Forward Obligation report and received this message: General SQL error. ORA-00907: missing right parenthesis. Terms: Let me know what you find. Thanks! & Kate, I ran the report with the exact same options and it came right up. Try it again, exactly as before. Usually if it works for one person and not the other it is a security issue. Let me know what happens. Thanks, Brettther & \num{0}{\%}  & yes               \\
      \hline
      Didn't you trade uranium at one time?                                                                                                                                                                 & Yeah, I know the buisness VERY well.                                                                                                                                                                                               & \num{0}{\%}  & no                \\
      \hline
      Are you free for drinks either Monday or Wednesday?                                                                                                                                                   & Yes                                                                                                                                                                                                                                & \num{0}{\%}  & no                \\
      \hline
      Mons, I would be available on the 25th, 26th or 27th. I cannot make it the week of the 18th. Thanks, Bill.                                                                                            & OK, so, let's see if we can get together later today. I have to leave at 16:00 for a few minutes, but I am sure that I will be out at that moment. Thank you Kim.                                                                  & \num{0}{\%}  & yes               \\
      \hline
    \end{tabularx}
  \end{table}
\end{frame}
%---------------------------------------------------------

@@

  \begin{itemize}
    \item \href{https://github.com/claudioscheer/seq2seq-bert}{https://github.com/claudioscheer/seq2seq-bert};
    \item \href{https://github.com/claudioscheer/seq2seq-bert/releases/tag/v0.0.8-alpha}{Final release (v0.0.8)};
  \end{itemize}
\end{frame}
%---------------------------------------------------------

>>>>

%---------------------------------------------------------
\section{Implementation}

  \begin{itemize}
    \item BERT base;
          \begin{itemize}
            \item 12 layers;
          \end{itemize}
    \item Hugging Face and PyTorch;
    \item NVIDIA T4 GPU on AWS;
          \begin{itemize}
            \item 16GB;
          \end{itemize}
  \end{itemize}
\end{frame}

@@

@@

  \begin{itemize}
    \item Adam;
          \begin{itemize}
            \item Adam epsilon: \num{1e-4};
          \end{itemize}
    \item Batch size: \num{10};
    \item Fine-tuning epochs: \num{10.5};
    \item Beam search hypothesis: \num{3};
  \end{itemize}
\end{frame}

@@

  \begin{table}
    \scriptsize
    \begin{tabularx}{\textwidth}{|X|X|c|c|}
      \hline
      \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?}   & \textbf{Was it AI?} \\
      \hline
      Let me know if this works.                                                                                                                                                                            & This works great. Will let you know. as soon as I get a chance, let me know                                                                                                                                                        & \num{100}{\%}  & yes                 \\
      \hline
      Following are the terms under which I ran the Forward Obligation report and received this message: General SQL error. ORA-00907: missing right parenthesis. Terms: Let me know what you find. Thanks! & Kate, I ran the report with the exact same options and it came right up. Try it again, exactly as before. Usually if it works for one person and not the other it is a security issue. Let me know what happens. Thanks, Brettther & \num{50}{\%}   & yes                 \\
      \hline
      Didn't you trade uranium at one time?                                                                                                                                                                 & Yeah, I know the buisness VERY well.                                                                                                                                                                                               & \num{33.3}{\%} & no                  \\
      \hline
      Are you free for drinks either Monday or Wednesday?                                                                                                                                                   & Yes                                                                                                                                                                                                                                & \num{66.7}{\%} & no                  \\
      \hline
      Mons, I would be available on the 25th, 26th or 27th. I cannot make it the week of the 18th. Thanks, Bill.                                                                                            & OK, so, let's see if we can get together later today. I have to leave at 16:00 for a few minutes, but I am sure that I will be out at that moment. Thank you Kim.                                                                  & \num{16.7}{\%} & yes                 \\
      \hline
    \end{tabularx}
  \end{table}
\end{frame}
%---------------------------------------------------------

@@

  \begin{itemize}
    \item \href{https://github.com/claudioscheer/seq2seq-bert}{https://github.com/claudioscheer/seq2seq-bert};
    \item \href{https://github.com/claudioscheer/seq2seq-bert/releases/tag/v0.0.8-alpha}{Final release (v0.0.8)};
    \item \href{https://www.kaggle.com/wcukierski/enron-email-dataset}{The Enron Email Dataset};
    \item \href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{Dataset parser};
  \end{itemize}
\end{frame}
%---------------------------------------------------------
